Tensor anisotropy as a tracer of cosmic voids

### 2015-03-12 cosmic_voids.tex
Little comment in conclusions
Acknowledgments

Put together, the results for the radially averaged profiles support the 
evidence for a universal density profile.  
This extends the work done
by \cite{Hamaus14} to smaller void sizes.

@@

We would like to thank Nelson Padilla for helpful comments and suggestions
on the manuscript.

>>>>

Put together, the results for the radially averaged profiles support the 
evidence for a universal density profile.  
This extends the work done
by \cite{Hamaus14} to smaller void sizes and by \cite{Ceccarelli13} for
the SDSS.

@@

We would like to thank Rien van de Weygaert for his thoughtful review and 
very helpful suggestions. Also, we thank Nelson Padilla for his comments 
on the manuscript. SB thanks Jaime Forero-Romero for all his support and 
guidance while developing this work. SB also thanks Juan Carlos Mu\~noz-Cuartas 
for many clarifying discussions and helpful ideas.
